\documentclass{article}

\author{Franco Colmenarez}
\title{R\'esum\'e}

\begin{document}

\maketitle

\section{Employment History}

\subsection{Software Developer, Dago}

Oct 2017 - Mar 2018, San Antonio, Edo. Miranda, Venezuela

Developing management systems with \textbf{Javascript (vanilla and jQuery), PHP (the company's own framework), PostgreSQL and Git}

\subsection{Software Developer, Aleli Inform\'atica}

Jul 2018 - Sep 2020, Paraguay (remotely)

Developing and maintaining multiple management systems with
\textbf{Git, PHP (Codeigniter and Laravel), Javascript (vanilla, jQuery and multiple libraries)}
and making an Android application with \textbf{React Native}

\section{Education}

\subsection{High School, Liceo San Jos\'e}

Sep 2009 - Sep 2014, Los Teques, Edo. Miranda, Venezuela

\begin{itemize}
    \item Basic programming fundamentals with BASIC language
\end{itemize}

\subsection{College, IUT-FRP}

Sep 2014 - Sep 2018

\begin{itemize}
    \item Programming fundamentals, such as recursion, binary trees, pointers, linked lists, etc.
    \item PHP Language
    \item Relational databases and SQL
\end{itemize}

\subsection{Online courses}

Multiple online courses at \textbf{Platzi} such as \textbf{Git, Github and Gitlab, Javascript, Regex, Linux Commands, Data Engineering, etc.}

\section{Skills}

\subsection{Languages}

Spanish (native), English (intermediate).

\subsubsection{Programming}

JavaScript, C/C++, PHP, JSX

\subsubsection{Libraries and Frameworks}

Vue.js, React.js, React Native, Laravel, HighCharts, MaterializeCSS, Bootstrap, TailwindCSS

\subsubsection{Markup}

{\LaTeX}, HTML, CSS, Markdown.

\subsubsection{Misc}

Linux commands, Regular Expressions, Object Oriented Programming, Functional Programming.

\subsection{Versioning}

Git, Github and Gitlab

\section{Hobbies}

I like to learn more about computing in general, learning new algorithms, and develop videogames in my spare times.

\section{Interested to learn:}

Low Level Programming, Reverse Engineering, Machine Learning, Security research

\end{document}
